%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[3]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[1.75pt]
    {#3} & & \\[9.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Bakhomious Basta} \\[7.5pt]
\href{https://github.com/bakhomious}{\raisebox{-0.05\height}\faGithub\ bakhomious} \ $|$ \
\href{https://linkedin.com/in/bakhomious-basta}{\raisebox{-0.05\height}\faLinkedin\ bakhomious-basta} \ $|$ \
\href{mailto:bakhomioussvp@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ bakhomioussvp@gmail.com} \ $|$ \
\href{tel:+36306541948}{\raisebox{-0.05\height}\faMobile \ +36306541948} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{About}

A multiparadigm programming enthusiast with experience in building scalable applications and designing efficient systems.
Passionate about optimizing performance and enhancing code quality through best practices and innovative solutions.

%Experience
\section{Work Experience}

\begin{joblong}
    {Software Engineer | Tata Consultancy Services}
    {June 2023 -- Present}
    {Budapest, Hungary}
\item Collaborating in an Agile team to develop and deliver new features for ERP and CMS systems using RESTful APIs.
\item Designed and developed an Authorization Server with Spring Security 6 for SSO Federated Auth, Client Credentials (M2M), and Resource Owner Password Grant. Paired with an API Gateway using Spring Cloud Gateway. Reducing latency by 50\% and solving 90\% of reported vulnerabilities.
\item Developed from scratch to production an Intranet Portal using Spring Boot 4, Redis, React 19, TypeScript, Docker and AWS services. Allowing 1000+ business partners to access information about their CMS system and monitor real-time data.
\item Automated release management process with TypeScript and Jenkins pipelines, reducing deployment sanity check time by 70\%.
\item Upgraded Java versions (11 → 21) and modernized legacy Spring 2.x codebases to 3.x standards.
\item Deploying and managing CI/CD pipelines using Jenkins, Spinnaker, AWS, and Istio.
\item Expanding backend APIs to handle complex business logic, improve architecture, and reduce technical debt.
\item Mentored frontend and backend tracks for the company's annual internship program.
\end{joblong}

\begin{joblong}
    {Undergraduate Teacher Assistant | University of Debrecen}
    {February 2023 - January 2024}
    {Debrecen, Hungary}
\item Instructed over 40 students in C and Java programming across various semesters, achieving a 60\% increase in success rate.
\item Received a research scholarship for conducting research on static code analysis in C language programs.
\item Prepared engaging lab materials encompassing a broad range of technologies, including Maven, Git, Jackson and Lombok. Introduced students to hands-on implementations of Data Structures and Algorithms.
\item Automated attendance tracking using RESTful APIs and university cards' QR code.
\item Automated grading of programming exams using language parsers, static code analysis and runtime evaluation.
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2021 - 2024 & Bachelor of Science in Computer Science | \textbf{University of Debrecen} \hfill (GPA: 4.75/5.0) \\
\end{tabularx}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item A Stipendium Hungaricum Scholarship holder.
\item First Place in the Scientific Students' Association Conference 2024.
\item Received Student Memorial Medal for academic excellence.
\end{itemize}

%----------------------------------------------------------------------------------------
%	CERTIFICATES
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2026 & \href{https://learn.microsoft.com/en-gb/users/bakhomiousbasta-0411/credentials/b5890c8acf53c73a}{\textbf{GitHub Copilot Certification}} | Microsoft Learn \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages &  \normalsize{Java, JavaScript/TypeScript, Python, SQL, Bash}\\
Technologies  &  \normalsize{Spring Boot, Docker, Git, AWS, Jenkins, SQS, Kibana, Maven}\\
\end{tabularx}

% \vfill
% \center{\footnotesize Last updated: \today}

\end{document}
